% Document template for ANS Journals
% Options: footnoteAtEnd - Places all footnotes at the end of document
%               Usage: \documentclass[footnoteAtEnd]{style/nseJournal}
\documentclass{nseJournal}
\usepackage{local}

\begin{document}

\title{Krylov Linear Solvers and Quasi Monte Carlo
Methods for Transport Simulations}

% Use the \addAuthor macro to add authors in the order they should appear. The second argument corresponds to
% the affiliation declared below.
\addAuthor{Sam Pasmann}{a}
\addAuthor{C. T. Kelley}{b}
\addAuthor{\correspondingAuthor{Ryan McClarren}}{a}
\correspondingEmail{rmcclarr@nd.edu}

% Affiliations can be added in the order they should appear. For breaks in addresses, use either \\ or \tabularnewline
\addAffiliation{a}{Department of Aerospace and Mechanical Engineering\\ University of Notre Dame\\ Fitzpatrick Hall, Notre Dame, IN 46556}
\addAffiliation{b}{North Carolina State University, Department of
Mathematics\\ 3234 SAS Hall, Box 8205\\ Raleigh NC 27695-8205}

% Add keywords to appear in Abstract in the order they should appear
\addKeyword{Quasi Monte Carlo Methods}
\addKeyword{Krylov Linear Solvers}

\titlePage

\begin{abstract}
The Boltzmann form of the neutron transport equation describes the behavior of neutrons as they collide from one atom to another and is important in nuclear reactor design and accident analysis. The full neutron transport equation is space, direction, time and energy dependent. In many cases an analytic solution cannot be solved unless many simplifying assumptions are made. Numerical methods must be relied upon to provide physically realistic solutions. Iterative methods, like the diffusion accelerate Source Iteration (SI) are a standard practice. These iterative methods can be enhanced by replacing the deterministic transport sweep with Monte Carlo (MC) simulation. This Hybrid method can be further enhanced using Quasi-Monte Carlo (QMC) techniques, reducing the noise inherent in MC simulations. However, the SI method can suffer from low convergence rates, particularly in optically thick media. Preconditioned Krylov Subspace methods provide a more efficient solution compared to the SI method. Krylov methods including GMRES and BiCGStab are shown to outperform the SI in several test problems using the outlined hybrid QMC-iterative solver method.  
\end{abstract}


\input{intro_Krylov_QMC}

\input{results_Krylov_QMC}

\clearpage


\section{Conclusion}
\label{sec:conclusion}


\pagebreak
\section*{Acknowledgments}

The research of CTK was supported by 
Department of Energy grant DE-NA003967,
%
and National Science Foundation Grants
% RTG
DMS-1745654,
and
% New NSF
DMS-1906446.


\pagebreak
\bibliographystyle{ans_js}                                                                           %custom ANS journal submission template bibliography style
\bibliography{qmckrylov}

\end{document}


