\section{Computational Results}
\label{sec:results}
In this section we consider an example from
\cite{cesinh}. The formulation of the transport
problem is taken from \cite{ctk:jeff1}. The equation for the angular
flux \(\psi\) is

\[
\mu \frac{\partial \psi}{\partial x} (x,\mu) + \Sigma_t(x) \psi(x,\mu) =
\frac{1}{2} \left[ \Sigma_s(x) \int_{-1}^1 \psi(x, \mu') \dmup + q(x) \right]
 \mbox{ for } 0 \le x \le \tau
\]

The boundary conditions are

\[
\psi(0, \mu) = \psi_l(\mu), \mu > 0; \psi(\tau, \mu) = \psi_r(\mu),
\mu < 0.
\]

The notation is

\begin{itemize}
\item
  \(\psi\) is intensity of radiation or angular flux at point \(x\) at
  angle \(\cos^{-1} (\mu)\)
\item
  \(\phi = \phi(x) = \int_{-1}^{1}\psi(x,\mu) \ d\mu\) is the scalar
  flux, the \(0^{th}\) angular moment of the angular flux. -
  \(\tau < \infty\), length of the spatial domain. -
  \(\Sigma_s \in C([0,\tau])\) is the scattering cross section at \(x\)
  - \(\Sigma_t \in C([0,\tau])\) is the total cross section at \(x\) -
  \(\psi_l\) and \(\psi_r\) are incoming intensities at the bounds -
  \(q \in C([0,\tau])\) is the fixed source
\end{itemize}


\subsection{The Garcia-Siewert Example}
\label{the-garcia-siewert-example}

In this example \[
\tau=5, \Sigma_s(x) =\omega_0 e^{-x/s},  \Sigma_t(x) = 1, q(x) = 0, \psi_l(\mu) = 1, \psi_r(\mu) = 0.
\]

\subsection{Solvers}
\label{subsec:solvers}

The linear and nonlinear solvers come from the Julia package
\href{https://github.com/ctkelley/SIAMFANLEquations.jl}{SIAMFANLEQ.jl}
\cite{ctk:siamfanl}. The documentation for these codes is in the
\href{https://github.com/ctkelley/NotebookSIAMFANL}{Juila notebooks}
that accompany the package \cite{ctk:notebooknl}. 
These are part of a book project \cite{ctk:fajulia}. 

\subsection{Source Iteration and Krylov Methods}
\label{source-iteration-and-krylov-methods}

We use two krylov methods \cite{ctk:roots}, GMRES \cite{gmres} and
Bi-CGSTAB \cite{bicgstab}.

\subsection{QMC}\label{qmc}

\subsection{Validation and calibration study}
\label{validation-and-calibration-study}

I'll compare the results from the SN computation to what I get from
Sam's QMC code. My SN results are for a very fine spatial mesh and fine
enough angular mesh. They are good to at least six figures and I will
regard them as exact for this study.

I will use the SN results for the table in the Garcia-Siewert paper and
get results from QMC in the following way

\begin{itemize}
\item
  For a give N and Nx I will get cell average fluxes from Sam's code.
\item
  I will use the same code to generate the tables that I used for the SN
  fluxes. That code is \textbf{src/sn\_tabulate.jl}
\item
  I will take the two 11 x 2 arrays of results DataSN and DataQMC and
  compoute componentwise relative error with
\end{itemize}

\begin{verbatim}
Derr = (DataSN-DataQMC)./DataSN
\end{verbatim}

\subsection{QMC and Krylov Linear Solvers}
\label{qmc-and-krylov-linear-solvers}

I can solve the QMC linear problem with both Krylov methods now and,
just like the classical case, I'm seeing fewer than half of the number
of transport sweeps. Herewith the results for N=1000 and Nx= 100.





